---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# titable

<!-- badges: start -->
<!-- badges: end -->

The `titable` package provides function to efficiently conduct logistic 
regression analyses, and summarize them into compact tables. These tables can be
saved in an excel sheet with a nice formatting. 

The raw results of logistic regression are also directly accessible in the form
of a data.frame. Thus, enabling, to achieve some usal plots as, for instance, 
forest plots.


## Installation

You can install the development version of titable from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("paul-bssr/titable", INSTALL_opts=c("--no-multiarch"))
```

Sometimes JAVA version can cause an issue, generating th efollowing error message :
```
Error : .onLoad failed in loadNamespace() for 'rJava', details:
   call: fun(libname, pkgname)
   error: JAVA_HOME cannot be determined from the Registry
 Error: package or namespace load failed for ‘rJava’
```
In that case, installing 64 bit Java ([here](https://java.com/en/download/manual.jsp)) 
should solve the issue.

## Example

This is a typical use case for the library:

```{r example}
library(titable)
## Generating a summary table
table <- summary_table(data = wdbc.data,
                       studied_vars = c("radius", "texture", "compactness_quartile"),
                       dependent = "diagnosis",
                       multivariate = list(c("smoothness", "texture"),
                                           c("concavity", "symmetry")),
                       digits = 2,
                       digits_p = 2,
                       p_limit=0.001,
                       verbose=FALSE
                       )
table

## Saving the result in an excel file
# # Creating an excel file
# save_summary_table(table, filepath="inst/extdata/", filename="test",
#                    sheetname = "test_sheet_1",
#                    title = "Regression logistic study",
#                    subtitle = "This is an interesting study.",
#                    list_variables_renaming = list("compactness_quartile"="Compactness quartile")
#                    )

```
